### 2021-12-12 thesis/tex/nsiResults.tex
update

\section{The NSI Hypothesis}\label{sec:constraining}
%TODO Ch 5.2 write what new things we have in the sterile analysis/chi2. Ie that NSI is showing in GeV -> deep core 
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
uncertainty.

@@

After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.

Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
% TODO: Write a few lines about the plots 5.4 and 5.5
\begin{figure}
   \begin{center}
      \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon. $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
   \end{center}
\end{figure}

%TODO: PINGU values are the same. Fill in empty values
{\renewcommand{\arraystretch}{1.0}
 \begin{table}
   \begin{center}
      \begin{tabular}{lcc}
         \hline
         Parameter & Best 90\% CL & Best $3\sigma$\\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.0080, 0.0090] &  [-0.014, 0.017]  \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
         $\emt$ &  [-0.0080, 0.0090] &  [-0.014, 0.017] \\
         $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] \\
         $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore} \\
         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
         \hline
         \vspace{2em}
      \end{tabular}
      \begin{tabular}{lcc}
         \hline
         Parameter & Baseline 90\% CL & Baseline $3\sigma$ \\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.0090, 0.010] &  [-0.015, 0.018]  \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &    [-0.046, 0.054] &  [-0.065, 0.073]  \\
         $\emt$ &     [-0.0090, 0.010] &  [-0.015, 0.018]  \\
         $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16]    \\
         $\eet$ &    [-0.10, 0.11] &  [-0.19, 0.18]  \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore}\\
         $\emt$ &   [-0.029, 0.0070] & [-0.041, 0.026] \\
         \hline
         \vspace{2em}
      \end{tabular}
      \begin{tabular}{lcc}
         \hline
         Parameter & Worst 90\% CL & Worst $3\sigma$\\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &   [-0.010, 0.011] &   [-0.017, 0.020] \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &    [-0.049, 0.057] &  [-0.070, 0.078] \\
         $\emt$ &     [-0.010, 0.011] &   [-0.017, 0.020] \\
         $\eem$ &   [-0.14, 0.11] &   [-0.23, 0.18] \\
         $\eet$ &   [-0.13, 0.13] &  [-0.23, 0.12] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore}\\
         $\emt$ &   [-0.029, 0.007] & [-0.041, 0.026] \\
         \hline
      \end{tabular}
      \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. $\dm[31]$ and $\theta_{23}$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero. Best, baseline, and worst refer to 
      the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
   \end{center}
\end{table}

\begin{table}
   \centering
   \begin{tabular}{lcc}
      \hline
      Parameter & Best 90\% CL & Best $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &  [-0.054, 0.067] & [-0.089, 0.10] \\
      $\emt$ &  [-0.029, 0.0070] & [-0.041, 0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
      $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013] \\
      $\eem$ &   [-0.060, 0.077] &  [-0.13, 0.13] \\
      $\eet$ &  [-0.052, 0.095] &  [-0.11, 0.14] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013]  \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Baseline 90\% CL & Baseline $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &   [-0.054, 0.067] & [-0.089, 0.10]\\
      $\emt$  &  [-0.029, 0.0070] & [-0.041, 0.026] \\
      $\eem$ &    [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &    [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
      $\emt$ &    [-0.010, 0.0060] &  [-0.016, 0.014] \\
      $\eem$ &    [-0.071, 0.086] &  [-0.15, 0.14]  \\
      $\eet$ &   [-0.061, 0.10] &  [-0.13, 0.16] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.010, 0.006] &  [-0.016, 0.014] \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &    [-0.054, 0.067] & [-0.089, 0.10] \\
      $\emt$ &    [-0.029, 0.007] & [-0.041, 0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &     [-0.039, 0.050] & [-0.06, 0.07] \\
      $\emt$ &  [-0.011, 0.0070] &  [-0.017, 0.015] \\
      $\eem$ &   [-0.082, 0.097] &  [-0.17, 0.16] \\
      $\eet$ &   [-0.067, 0.11] &  [-0.15, 0.17] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.011, 0.0070] &  [-0.017, 0.015] \\
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. $\dm[31]$ and $\theta[23]$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
   Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

%TODO: compare results

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm[31]$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm[31]$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
\newpage

@@

%TODO 5.6 is small, fix labels
There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI. For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the 
interaction Lagrangian respects lepton flavor conservation. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
but this is not feasible. Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$. We let $\ett=0$ because we saw that it did not influence the other parameters. 
We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}. We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical. 
Hence, we can see that no relationship exists between them. With $\eet - \eem$, however, the contours are assuming a different shape. The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.
Thus, we can draw the conclusion that, given $\ett = 0$, PINGU might expect to observe that $\eem$ and $\emt$ are anti-correlated while we expect no significant correlation
to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$. This is consistent with our observation of the effect of these parameters on $\Pme$ in  Fig.~\ref{fig:eem_eet_prob}, from which we 
saw that $\eem$ and $\eet$ strongly affect $\Pme$ for single-digit \si{\GeV} energies.

>>>>

\section{The NSI Hypothesis}\label{sec:constraining}
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$. As we shall see, the impacts of NSI mainly manifesting 
themselves at \si{\GeV} energies, causing us to bring back DeepCore and PINGU. We will consider the results obtained from these three detectors separately as well as jointly.

For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
uncertainty.

@@

After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}. Each region is bounded
by the best and worst case scenario, as defined in Table~\ref{table:syst_errors}, while the middle line is the baseline scenario. We again emphasize that 
no scenarios are considered for DeepCore, since they already provided in the data release~\cite{DC2019data}.

Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
Moreover, we see that we can expect PINGU to be sensitive to systematic uncertainty, especially when constraining $\eem$ and $\eet$ from the negative side.

\begin{figure}
   \begin{center}
      \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon. $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero. Dotted lines are the 90\% and $3\sigma$ CL levels.
    The zones contain the three uncertainty scenarios considered, and we see that the inclusion of PINGU is expected 
    to drastically make the bound on $\emt$ more stringent.
    }\label{fig:IC_3D}
   \end{center}
\end{figure}

{\renewcommand{\arraystretch}{1.0}
 \begin{table}
   \begin{center}
      \begin{tabular}{lcc}
         \hline
         Parameter & Best 90\% CL & Best $3\sigma$\\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.012, 0.011] &  [-0.017, 0.016] \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
         $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
         $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore} \\
         $\emt$ &  [-0.013, 0.0070] &  [-0.017, 0.013] \\
         \hline
         \vspace{2em}
      \end{tabular}
      \begin{tabular}{lcc}
         \hline
         Parameter & Baseline 90\% CL & Baseline $3\sigma$ \\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.015, 0.014] &  [-0.022, 0.021] \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
         $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
         $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore}\\
         $\emt$ &  [-0.016, 0.0070] &  [-0.022, 0.016] \\
         \hline
         \vspace{2em}
      \end{tabular}
      \begin{tabular}{lcc}
         \hline
         Parameter & Worst 90\% CL & Worst $3\sigma$\\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.018, 0.017] &  [-0.025, 0.024] \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &  [-0.054, 0.067] &  [-0.089, 0.10] \\
         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
         $\eem$ &  [-0.11, 0.15] &  [-0.23, 0.24] \\
         $\eet$ &   [-0.084, 0.15] &  [-0.188, 0.212] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore}\\
         $\emt$ &  [-0.018, 0.0070] &  [-0.024, 0.018] \\
         \hline
      \end{tabular}
      \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. $\dm[31]$ and $\theta_{23}$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero. Best, baseline, and worst refer to 
      the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
   \end{center}
\end{table}

\begin{table}
   \centering
   \begin{tabular}{lcc}
      \hline
      Parameter & Best 90\% CL & Best $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] \\
      $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.138] \\
      $\eet$ &  [-0.079, 0.098] &  [-0.148, 0.161] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
      $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013] \\
      $\eem$ &   [-0.060, 0.077] &  [-0.13, 0.13] \\
      $\eet$ &  [-0.052, 0.095] &  [-0.11, 0.14] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &  [-0.0080, 0.0050] &  [-0.012, 0.011] \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Baseline 90\% CL & Baseline $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &  [-0.046, 0.054] &  [-0.065, 0.073] \\
      $\emt$ &   [-0.0090, 0.010] &  [-0.015, 0.018] \\
      $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16] \\
      $\eet$ &   [-0.10, 0.11] &  [-0.19, 0.18] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
      $\emt$ &    [-0.010, 0.0060] &  [-0.016, 0.014] \\
      $\eem$ &    [-0.071, 0.086] &  [-0.15, 0.14]  \\
      $\eet$ &   [-0.061, 0.10] &  [-0.13, 0.16] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &  [-0.009, 0.0060] &  [-0.014, 0.012] \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &  [-0.049, 0.057] &   [-0.07, 0.078] \\
      $\emt$ &   [-0.01, 0.011] &   [-0.017, 0.02] \\
      $\eem$ &   [-0.137, 0.11] &   [-0.228, 0.18] \\
      $\eet$ &  [-0.132, 0.125] &  [-0.226, 0.196] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &   [-0.039, 0.050] &    [-0.060, 0.070] \\
      $\emt$ &  [-0.011, 0.0070] &  [-0.017, 0.015] \\
      $\eem$ &  [-0.082, 0.097] &  [-0.168, 0.16] \\
      $\eet$ &  [-0.067, 0.11] &  [-0.15, 0.17] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.010, 0.0060] &  [-0.016, 0.013] \\
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. $\dm[31]$ and $\theta[23]$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
   Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm[31]$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm[31]$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}

We compare our results to a similar analysis performed on the same DeepCore dataset in~\cite{demidov}. In that publication, 
the constraints found at 90\% CL were 
\begin{align}\label{eq:demidov}
   -0.055 <&\, \ett < 0.056 \nonumber \\
   -0.023 <&\, \emt < 0.016 \nonumber \\
   -0.21 <&\, \eem < 0.20 \nonumber \\
   -0.19 <&\, \eet < 0.20\,.
\end{align}
Comparing~\ref{eq:demidov} to our results from Table~\ref{table:IC_DC_results} at 90\% CL, namely
\begin{align}\label{eq:DC_results}
   -0.054 <&\, \ett < 0.067 \nonumber \\
   -0.029 <&\, \emt < 0.0070 \nonumber \\
   -0.12 <&\, \eem < 0.15 \nonumber \\
   -0.084 <&\, \eet < 0.15\,,
\end{align}
we see that our results for $\eem$, $\eet$ are more stringent, while the results for $\emt$ and $\ett$ are similar but more lenient. It is worth noting that the 
results from~\cite{demidov} are have been obtained by including more systematic uncertainties, such as the spectral index, hadron production, and baryon resonance. 
However, the overall flux normalization in~\cite{demidov} is 20\%, while we opted for a slightly higher figure of 25\% which could compensate for the exclusion of the 
statistical uncertainties mentioned.

Using the baseline case of 3\% systematic uncertainty at 90\% CL, we find from Table~\ref{table:PINGU_joint_results}, that our predictions for the proposed PINGU detector are
\begin{align}\label{eq_P_results}
   -0.049 <&\, \ett < 0.057 \nonumber \\
   -0.010 <&\, \emt < 0.011 \nonumber \\
   -0.137 <&\, \eem < 0.11 \nonumber \\
   -0.132 <&\, \eet < 0.125\,,
\end{align}
which displays an improvement over the DeepCore results in Eq.~\ref{eq:DC_results}, except for $\eet$ which is worse.

Finally, the joint results for $\emt$ using IceCube and DeepCore from~\ref{table:PINGU_joint_results} at 90\% CL are
\begin{align}\label{eq:ID_result}
   -0.016 <&\, \emt < 0.0070\,,
\end{align}
and when combining IceCube, DeepCore, and PINGU, the 90\% CL constraint on $\emt$ in our baseline scenario is predicted to be
\begin{align}\label{eq:PID_result}
   -0.010 <&\, \emt < 0.0060\,,
\end{align}
which is more stringent for $\emt>0$ than the result in~\cite{deepcoreNSI}.
\newpage

@@

There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI. For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the 
interaction Lagrangian respects lepton flavor conservation. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
but this is not feasible. Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$. We let $\ett=0$ because we saw that it did not influence the other parameters. 
We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}. We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical. 
Hence, we can see that no relationship exists between them. With $\eet - \eem$, however, the contours are assuming a different shape. The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.
Thus, we can draw the conclusion that, given $\ett = 0$, PINGU might expect to observe that $\eem$ and $\emt$ are anti-correlated while we expect no significant correlation
to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$. This is consistent with our observation of the effect of these parameters on $\Pme$ in  Fig.~\ref{fig:eem_eet_prob}, from which we 
saw that $\eem$ and $\eet$ strongly affect $\Pme$ for single-digit \si{\GeV} energies.

### 2021-12-12 thesis/tex/nsiTheory.tex
update

\subsection{IceCube Signal}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
the IceCube data is available in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have averaged out.

@@

\subsection{DeepCore and PINGU Signals}
Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
many oscillations have averaged out.

>>>>

\subsection{IceCube Signal}
The effect of NSI on the IceCube event count has been previously discussed in~\cite{salvadoNSI, DC2021, nsiFarzan}
In our analysis of IceCube, we are constrained to muon track events. Thus, we are not able to test any theory which does not modify $P_{\a \mu}$. Moreover,
the IceCube data is available in the range \SI{500}{\GeV} to \SI{10}{\TeV} range, where any rapid oscillations have averaged out.

@@

\subsection{DeepCore and PINGU Signals}
The effect of NSI on the DeepCore event count has been previously discussed in~\cite{smirnovNSI}, while the NSI effect 
in PINGU has been studied in~\cite{choubey2014, ohlsson2013}.
Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
will be more apparent, since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
many oscillations have averaged out.

### 2021-12-12 thesis/tex/sterileResults.tex
update

\subsection{Sterile Mass and Mixing}
Let us start with looking at the best-fit event distribution resulting from the $\chi^2$ minimization.
Fig.~\ref{fig:final_rate_plot} now contains the best-fit event distribution assuming the 3+1 hypothesis.
The best-fit values are $\dm[41] = \SI{0.01}{\eV\squared}$ and 
$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). %TODO: double check these
The contour plot shown in Fig.~\ref{fig:error_tuning} divides the parameter space into two regions.
To the right of the boundary, the $\Delta \chi^2$ has values above the confidence level, meaning that 
those parameter pairs can be excluded at a certain confidence level.

@@

In Fig.~\ref{fig:final_rate_plot}, we see that the simulations are consistent with the 3+0 hypothesis with deviations of 6\% at high single-digit 
\si{\TeV} energies.
Wanting to investigate the effect of $\theta_[34]$, we also simulated the 3+1 hypothesis using $\theta_[24] = \theta_[34]$. However, we did not see 
a difference in the exclusion regions compared to the regions when $\theta_[34] = 0$. Thus, we conclude that on our work, IceCube was not able to 
distinguish any effect due to the $\theta_[34]$ parameter.

>>>>

\subsection{Sterile Mass and Mixing}
Let us start with looking at the best-fit event distribution resulting from the $\chi^2$ minimization.
Fig.~\ref{fig:final_rate_plot} now contains the best-fit event distribution assuming the 3+1 hypothesis.
The best-fit values are $\dm[41] = \SI{0.01}{\eV\squared}$ and 
$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). 
The contour plot shown in Fig.~\ref{fig:error_tuning} divides the parameter space into two regions.
To the right of the boundary, the $\Delta \chi^2$ has values above the confidence level, meaning that 
those parameter pairs can be excluded at a certain confidence level.

@@

In Fig.~\ref{fig:final_rate_plot}, we see that the simulations are consistent with the 3+0 hypothesis with deviations of 6\% at high single-digit 
\si{\TeV} energies.
Wanting to investigate the effect of $\theta_{34}$, we also simulated the 3+1 hypothesis using $\theta_{24} = \theta_{34}$. However, we did not see 
a difference in the exclusion regions compared to the regions when $\theta_{34} = 0$. Thus, we conclude that on our work, IceCube was not able to 
distinguish any effect due to the $\theta_{34}$ parameter.
